Demographics: The Sound of Teaching Music 1

### 2020-07-29 script/RNotebook/articulation.Rmd
define filenames separately
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r extract, include = FALSE}
df_ioi <- read.csv("./trimmed/data_ioi.csv", header = T, sep = ",", dec = ".") # read a trimmed csv
df_kot <- read.csv("./trimmed/data_kot.csv", header = T, sep = ",", dec = ".") # read a trimmed csv

>>>>

```{r file, include = FALSE}
filename_ioi = "../R/trimmed/data_ioi.csv"
filename_kot = "../R/trimmed/data_kot.csv"
```

```{r extract, include = FALSE}
df_ioi <- read.csv(filename_ioi, header = T, sep = ",", dec = ".") # read a trimmed csv
df_kot <- read.csv(filename_kot, header = T, sep = ",", dec = ".") # read a trimmed csv

### 2020-07-29 script/RNotebook/dynamics.Rmd
define filenames separately
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r extract, include = FALSE}
df_vel <- read.csv("./trimmed/data_vel.csv", header = T, sep = ",", dec = ".") # read a trimmed csv
df_vel_acc <- read.csv("./trimmed/data_vel_acc.csv", header = T, sep = ",", dec = ".") # read a trimmed csv

>>>>

```{r file, include = FALSE}
filename_vel = "../R/trimmed/data_vel.csv"
filename_vel_acc = "../R/trimmed/data_vel_acc.csv"
```

```{r extract, include = FALSE}
df_vel <- read.csv(filename_vel, header = T, sep = ",", dec = ".") # read a trimmed csv
df_vel_acc <- read.csv(filename_vel_acc, header = T, sep = ",", dec = ".") # read a trimmed csv

### 2020-07-29 script/RNotebook/ioi.Rmd
define filenames separately
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r extract, include = FALSE}
df_ioi <- read.csv("./trimmed/data_ioi.csv", header = T, sep = ",", dec = ".") # read a trimmed csv

>>>>

```{r file, include = FALSE}
filename_ioi = "../R/trimmed/data_ioi.csv"
```

```{r extract, include = FALSE}
df_ioi <- read.csv(filename_ioi, header = T, sep = ",", dec = ".") # read a trimmed csv

### 2020-07-29 script/RNotebook/questionnaire.Rmd
define filenames separately
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r read, echo = FALSE}
# Read csv files
df <- read.csv("./questionnaire.csv", header = T, sep = ",", dec = ".", na.string = "NA")
df_exc <- read.csv("./filtered/data_errorRate.csv", header = T, sep = ",", dec = ".")
include <- df_exc$SubNr[df_exc$Final == "include"]

>>>>

```{r file, include = FALSE}
filename_que = "./questionnaire.csv"
filename_exc = "../R/filtered/data_errorRate.csv"
```

```{r read, echo = FALSE}
# Read csv files
df <- read.csv(filename_que, header = T, sep = ",", dec = ".", na.string = "NA")
df_exc <- read.csv(filename_exc, header = T, sep = ",", dec = ".")
include <- df_exc$SubNr[df_exc$Final == "include"]
